Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-10-13 09_Article/01_Revision1_Reviewers/Response to Reviewers_01.tex

References\vspace{-1em}
\begin{enumerate}
	\item Martin, E., Shapiro, J.R., 2007. Osteogenesis imperfecta: Epidemiology and pathophysiology. Curr Osteoporos Rep 5, 91–97. URL: http://www.le.ac.uk/genetics/collagen/.
	\item E, P., J, S.M., N, H.E., C, M.G., A, N.M., A, K.J., 2006. The population burden of fractures originates in women with osteopenia, not osteoporosis. Osteoporos Int 17, 1404–1409. doi:10.1007/s00198-006-0135-9.
\end{enumerate}

As for Reviewer \#1, Comment 1.1 and Comment 2.1\par

Introduction, Page2, Lines 44-45
\begin{quote}
	Therefore, the present study aims to compare trabecular bone microstructure of healthy and OI bone samples and to test the hypothesis of similar fabric-elasticity relationships.\Add{ Similar fabric-elasticity relationships will allow to extend the application of HR-pQCT-based hFE of healthy bone to OI bone at least in the linear elastic regime.}
\end{quote}

\newpage
\subsection{Methods - Participants}
\RC Could you add statistics about body anthropometry? I was wondering, why the groups were matched considering age and not height and weight? Could you explain your choice?

@@

\subsection{Methods - Image analysis}
\RC Page 3, lines 34-35, left column. The stack was divided into two halves WITH A TRANSVERSE PLANE. Pag 3, lines 4-7, right column. Did you use any filter to reduce the noise? If yes, please specify the procedure. Pag 4, line 4. Does your concern about the rotation consist in the errors associated with interpolation?

\AR The transverse plane precision is added to the manuscript. Yes a filtering is used in the standard image processing. The filtering procedure is added to the manuscript as shown below.\par

Methods - Image analysis, Page 2, Line 62, Right column
\begin{quote}
	Briefly, an automatic contouring algorithm was applied to define the periosteal contour of the tibia (masking)\Add{. Then, a Gauss filtering (sigma = 0.8, support = 1 voxel) was performed} and a threshold was applied for segmentation of cortical bone (450 mgHA/cm\textsuperscript{3}) and trabecular bone (320 mgHA/cm\textsuperscript{3}).
\end{quote}

Yes again, by keeping the ROI in its original configuration, errors due to interpolation are avoided. This is now precised in the manuscript.\par

@@

\AR The manuscript is modified in consequence:\par

Methods - Linear Regression, Page 4, Lines 47-48, Right column
\begin{quote}
	The orthotropic stiffness tensors obtained after transformation onto fabric coordinate system were then used to perform a multiple linear regression with the Zysset-Curnier model \Add{using the entire sample of both groups}.
\end{quote}

\subsection{Methods - Data filtering}
\RC You removed the regions that violated the assumption of homogeneity. Could this affect the final findings of the study? I mean, could this filtering remove the specimens with OI type IV?

\AR The first part of this question is closely related to Comment 1.2 of Reviewer \# 1. We would suggest to refer to our answer to this comment. For the second part, we would suggest to look at the plots used to answer to your comment 2.2. The filtering does not remove completely a specific OI type.

@@

		\multirow{3}{*}{ln(CV)} & Healthy & -1.723 $\pm$ 0.344 & & \multirow{3}{*}{-} & & \multirow{3}{*}{-} & & \multirow{3}{*}{-} &  \\
		& \multirow{2}{*}{OI} & \multirow{2}{*}{-1.178 $\pm$ 0.441} & \multirow{2}{*}{<0.0001} & & & & & & \\
		& & & & & & & & & \\

		\bottomrule
	\end{tabular}}
	OI types included in the study: Present study, types I and IV; Folkestad et al. [9], type I; Kocijan et al. [16], 1) type I 2) type III and IV; Rolvien et al. [26], type I and IV.
\end{sidewaystable*}

\newpage
\subsection{Results - Comparison with literature}
\RC Could you perform a test to evaluate if differences exist among the different regressions?

\AR As the full data sets of the other studies are not available, it is not possible to perform a statistical test to see if the stiffness constants i.e. the slopes are different. Nevertheless, it is possible to perform statistical tests on BV/TV, DA and NE (for filtered data sets), assuming they were normally distributed. These tests will only provide insights about differences in the explanatory variables and the fit quality but not about differences in the slopes (stiffness constants). As said in the discussion, these differences derive from the different scan resolutions between the two studies.

@@

\subsection{Discussion}
\RC The discussion is interesting and full of details and rigorous considerations. However, it is based only on the engineering/mathematical approach used in the study, and far from the clinical audience. I would like to read more about the effects of the different OI types in the provided findings.

\AR Thank you for your remark. The main idea of this study was to determine if standard hFE analyses could be performed on OI individuals. As shown in Figure \ref{02_OITypes}, there is no strict differences between OI type I and IV. Moreover, as filtering leaved only one ROI of OI type III, it is not possible to perform statistics about it. However, this one ROI is not different to the other ROIs kept after filtering. So the main conclusion of the present article is that when the ROI has enough mass (BV/TV) for homogenization to make sense, the distribution of this mass (fabric-elasticity relationship) is similarly optimized either in OI (type I, III, IV) or healthy trabecular bone. This means that standard hFE analyses can be performed by clinicians even if the patient is OI diagnosed, whatever the type, because it will not have a significant difference on the bone stiffness assessment.
